Ship-based lidar evaluation of Southern Ocean clouds in the storm-resolving general circulation model ICON, and the ERA5 and MERRA-2 reanalyses

### 2024-12-12 manuscript_agu.tex
Dataset reference

The Automatic Lidar and Ceilometer Framework (ALCF) is a ground-based lidar simulator and a tool for processing observed lidar data, supporting various instruments and models \cite{kuma2021}. It performs radiative transfer calculations to derive equivalent lidar AVBC in an atmospheric model, which can then be compared with observed AVBC. For this purpose, it takes the cloud fraction, liquid and ice mass mixing ratio, temperature, and pressure model fields as an input and is run offline (on the model output rather than inside the model code). The lidar simulator in the ALCF is based on the instrument simulator Cloud Feedback Model Intercomparison Project (CFMIP) Observation Simulator Package (COSP) \cite{bodas-salcedo2011}. After AVBC is calculated, a cloud mask, cloud occurrence by height, and the total cloud fraction are determined. The ALCF has been used by several research teams for model and reanalysis evaluation \cite{kuma2020,kremser2021,guyot2022,pei2023,whitehead2023,mcdonald2024}.

@@

The RV \emph{Polarstern} datasets are openly available on Pangaea (\url{https://pangaea.de}), as listed in Table~\ref{tab:voyage-references}. The MARCUS and MICRE datasets are openly available from ARM (\url{https://www.arm.gov}). The MERRA-2 data are openly available from the NASA Goddard Earth Sciences (GES) Data and Information Services Center (DISC) (\url{https://disc.gsfc.nasa.gov/datasets?project=MERRA-2}). The ERA5 data are openly available from the Copernicus Climate Data Store (CDS) (\url{https://cds.climate.copernicus.eu}). The ICON data are available on the Levante cluster of the DKRZ (\url{https://www.dkrz.de/en/systems/hpc/hlre-4-levante}) after registration at \url{https://luv.dkrz.de/register/}. The CERES products are openly available from the project website (\url{https://ceres.larc.nasa.gov}) and the NASA Atmospheric Science Data Centre (\url{https://asdc.larc.nasa.gov/project/CERES}). The TAN1802 data are openly available on Zenodo \cite{kremser2020}. The code for performing the presented analysis and precipitation detection is open-source and available at \url{https://github.com/peterkuma/icon-so-2024} and \url{https://github.com/peterkuma/alcf-precip}, respectively. The remaining voyage data (AA15-16, HMNZSW16, NBP1704, TAN1502, and TAN1702) are openly available on Zenodo (\url{https://doi.org/}).

>>>>

The Automatic Lidar and Ceilometer Framework (ALCF) is a ground-based lidar simulator and a tool for processing observed lidar data, supporting various instruments and models \cite{kuma2021}. It performs radiative transfer calculations to derive equivalent lidar AVBC in an atmospheric model, which can then be compared with observed AVBC. For this purpose, it takes the cloud fraction, liquid and ice mass mixing ratio, temperature, and pressure model fields as an input and is run offline (on the model output rather than inside the model code). The lidar simulator in the ALCF is based on the instrument simulator Cloud Feedback Model Intercomparison Project (CFMIP) Observation Simulator Package (COSP) \cite{bodas-salcedo2011}. After AVBC is calculated, a cloud mask, cloud occurrence by height, and the total cloud fraction are determined. The ALCF has been used by several research teams for model and reanalysis evaluation \cite{kuma2020,kremser2021,guyot2022,pei2023,whitehead2023,mcdonald2024a}.

@@

The RV \emph{Polarstern} datasets are openly available on Pangaea (\url{https://pangaea.de}), as listed in Table~\ref{tab:voyage-references}. The MARCUS and MICRE datasets are openly available from ARM (\url{https://www.arm.gov}). The MERRA-2 data are openly available from the NASA Goddard Earth Sciences (GES) Data and Information Services Center (DISC) (\url{https://disc.gsfc.nasa.gov/datasets?project=MERRA-2}). The ERA5 data are openly available from the Copernicus Climate Data Store (CDS) (\url{https://cds.climate.copernicus.eu}). The ICON data are available on the Levante cluster of the DKRZ (\url{https://www.dkrz.de/en/systems/hpc/hlre-4-levante}) after registration at \url{https://luv.dkrz.de/register/}. The CERES products are openly available from the project website (\url{https://ceres.larc.nasa.gov}) and the NASA Atmospheric Science Data Centre (\url{https://asdc.larc.nasa.gov/project/CERES}). The TAN1802 data are openly available on Zenodo \cite{kremser2020}. The code for performing the presented analysis and precipitation detection is open-source and available at \url{https://github.com/peterkuma/icon-so-2024} and \url{https://github.com/peterkuma/alcf-precip}, respectively. The remaining voyage data (AA15-16, HMNZSW16, NBP1704, TAN1502, and TAN1702) are openly available on Zenodo \cite{mcdonald2024b}.
